### 2019-11-27 paper/paper.tex
cite
added abstract

\section{Introduction}
There are now many neural network methods and architectures designed for 
image classification that perform exceptionaly well. These models were trained
on millions of images, with powerful GPU acceleration. However in many cases where
an individual or group needs a model for an image classification task, these pretrained
models do cannot be applied directly. In this case, the usual solution is to use transfer learning.
Using the pretrained model as a feature extractor, we pass our task specific data into a 
pretrained model and then train a linear classifier using the extracted features of our images.

@@

\begin{tabular}{|c|c|c|c|c|}
    \hline\\
     &Model1 & Model2&Model3&Model4 \\
     \hline\\
     Error&0.229&0.565&0.314&0.236\\
     \hline\\
     Accuracy&0.946&0.932&0.927&0.936\\
      \hline
     F1 Score&0.321&0.169&0.312&0.267\\
     \hline
\end{tabular}

>>>>

\section*{Abstract}
Transfer learning is a popular method for tackling machine learning problems with image classification, 
pretrained models alows people to leverage it's generalization capabilities without needing large compute 
resources. In this project, we focused on models to classify images of mixed patterns of proteins,
taken with a microscope. To achieve this goal, we utilized transfer learning 
and demonstrated the hypothesis that earlier layers in a convolutional network captures simple features,
while later layers captures more complex features. Due to the differences between the training set
of the pretrained model and our dataset, we show that ealier layers in a pretrained convolutional network
gives better results in our classification task. Our best model realized a 94\% accuracy on 
the test dataset with limited computational sources, thus provided a feasible way for people with 
no powerful machines.
\section{Introduction}
There are now many neural network methods and architectures designed for 
image classification that perform exceptionaly well. These models were trained
on millions of images, with powerful GPU acceleration. However in many cases where
an individual or group needs a model for an image classification task, these pretrained
models do cannot be applied directly. In this case, the usual solution is to use transfer learning.
Using the pretrained model as a feature extractor, we pass our task specific data into a 
pretrained model and then train a linear classifier using the extracted features of our images.

@@

\begin{tabular}{|c|c|c|c|c|}
    \hline\\
     Model1 & Model2&Model3&Model4 \\
     \hline\\
     Error&0.229&0.565&0.314&0.236\\
     \hline\\
     Accuracy&0.946&0.932&0.927&0.936\\
      \hline
     F1 Score&0.321&0.169&0.312&0.267\\
     \hline
\end{tabular}
